### 2018-04-10 Sections/encrypted_cloud_quantum_computing.tex
Added to Section XXIII

\subsection{Classical computation} \index{Classical encrypted computation}
\comment{To do!}

\comment{Summarise state of knowledge on homomorphic classical computation, and blind computation. How much do they hide? What is the scaling of computational resource overhead? What limitations do they face?}

\comment{If not too complicated, sketch an outline of the protocol in an Alg. box.}

\comment{A universal QC can implement any classical algorithm. So QCs with homo/BQC give us the means by which to perform encrypted classical computations, bypassing limitations imposed by purely classical protocols.}
\sihui{[Comment: The polynomial hierarchy is not contained in BQP. In fact, NP-complete problems are not contained in BQP.]}

@@

\sihui{The specifics of these algorithm vary from scheme to scheme, and as in the case of FHE, usually contains sub-algorithms within them.}

>>>>

\subsection{Classical computation} \index{Classical encrypted computation}
\comment{A universal QC can implement any classical algorithm. So QCs with homo/BQC give us the means by which to perform encrypted classical computations, bypassing limitations imposed by purely classical protocols.}
\sihui{[Comment: The polynomial hierarchy is not contained in BQP. In fact, NP-complete problems are not contained in BQP.]}

@@

\sihui{The specifics of these algorithm vary from scheme to scheme, and as is in the case of FHE, usually contains sub-algorithms within them. Making FHE practical is an active area of research. Much of the problem lies in the bootstrapping required in Gentry's scheme, and some of these efforts lies in reducing the overhead required in bootstrapping or removing the need for bootstrapping entirely. Although there exists a plethora of FHE schemes, they are based mainly on two types of problems in lattice-based cryptography: the Shortest Vector Problem (SVP), and Learning with Errors (LWE) Problem. Gentry's original FHE was based on SVP, but over time, the schemes have moved towards a LWE approach because they offer lower overhead and are conceptually simpler . An overview of advances, and applications of homomorphic encryption can be found in a recent review \cite{bib:Halevi2017}.}
